NMRlipids Databank: Overlay Databank of Lipid Membrane Simulations Arising from Open Collaboration

### 2022-08-15 main.tex
Update text

\begin{table}[]
    \centering
    \begin{tabular}{  p{3.5cm}  p{9.5cm}  p{4.0cm} }
    \toprule
    key & description & type  \\
    \midrule
        %\hline
    DOI & DOI from where the raw data is found & user given (compulsory) \\
    SOFTWARE & Software used to run the simulation (e.g. Gromacs, Amber, NAMD, etc.) & \\
    TRJ & Name of the trajectory file found from DOI & \\
    TPR & Name of the topology file found from DOI (trp file in the case of Gromacs) & \\
    PREEQTIME & Pre-equilibrate time simulated before the uploaded trajectory in nanoseconds. \tablefootnote{For example, if you upload 100-200 ns part of total 200 ns simulation, this should value should be 100.} & \\
    TIMELEFTOUT & Equilibration period in the uploaded trajectory that should be discarded in analyses. \tablefootnote{For example, if you upload 0-200 ns part of total 200 ns simulation where the first 100 ns should be considered as an equilibration, this value should be 100.} \\
    COMPOSITION & Molecules names used in the simulation and corresponding mapping files (see ??) & \\
    DIR\_WRK & Temporary working directory in your local computer. \\
    UNITEDATOM\_DICT & Information for constucting hydrogens for united atom simulations, empty for all atom simulations & \\
    TYPEOFSYSTEM & Lipid bilayer or something else & \\
    \hline
    PUBLICATION & Give reference to a publication(s) related to the data. & User given (optional)\\
    AUTHORS\_CONTACT & Name and email of the main author(s) of the data. & \\
    SYSTEM & System description on free text format & \\
    SOFTWARE\_VERSION & Version of the used software & \\
    FF & Name of the used force field & \\
    FF\_SOURCE & Source of the force field parameters, e.g, CHARMM-GUI, webpage, citation to a publication, etc. & \\
    FF\_DATE &  Date when force field parameters were accessed on the gives source (day/month/year). & \\
    FF{molename} & Molecule specific force field information, e.g., water model with FFSOL and sodium parameters with FFSOD. & \\
    CPT & Name of the Gromacs checkpoint file. & \\
    LOG & Name of the Gromacs log file. & \\
    TOP & Name of the Gromacs top file. & \\
    GRO & Name of the Gromacs gro file. & \\
    \hline
    TRAJECTORY\_SIZE & Size of the trajectory file in bytes & automatically extracted data. \\
    TRJLENGTH & Lenght of the trajectory (ps). & \\
    TEMPERATURE & Temperature of the simulation. & \\
    NUMBER\_OF\_ATOMS & Number of atoms in the simulation. & \\
    DATEOFRUNNIG & Date when added into the databank & \\
    EXPERIMENT & Potentially connected experimental data & \\
    COMPOSITION & Numbers of lipid molecules (NPOPC, NPOPG, etc.) per membrane leaflet are calculated by determining on which side of the center of mass of the membrane the center of mass of the head group of each lipid molecule is located.
    Numbers of other molecules such as solvent and ions (NSOL, NPOT, NSOD, etc.) are read from the topology file. & \\
    \end{tabular}
    \caption{Keys stored in the README.yaml files of simulations.}
    \label{tab:READMEkeys}
\end{table}

@@

\begin{table}[]
    \centering
    \begin{tabular}{  p{5.0cm}  p{10.0cm}}
    \toprule
    key & description \\
    \midrule
    DOI & DOI of the publication related to the experimental data. \\
    TEMPERATURE & Temperature of the experiment. \\
    MOLAR\_FRACTIONS & Dictionary of molar fractions of bilayer components \\
    ION\_CONCENTRATIONS & Dictionary of ion concentrations of the system (defined as ??) \\
    TOTAL\_LIPID\_CONCENTRATION & Total concentration of lipid components. If exact concentration is not known, but experiments are performed in excess water, 'full hydration' can be given. \\
    COUNTER\_IONS & Type of counter ions if present.
\end{tabular}
    \caption{Keys stored in the README.yaml files of experiments.}
    \label{tab:READMEkeysEXP}
\end{table}

@@

\subsection{Molecule and atom naming convention}

>>>>

\begin{table}[]
    \centering
    \begin{tabular}{  p{3.5cm}  p{9.5cm}  p{4.0cm} }
    \toprule
    key & description & type  \\
    \midrule
        %\hline
    DOI & DOI from where the raw data is found & user given (compulsory) \\
    SOFTWARE & Software used to run the simulation (e.g. Gromacs, Amber, NAMD, etc.) & \\
    TRJ & Name of the trajectory file found from DOI & \\
    TPR & Name of the topology file found from DOI (trp file in the case of Gromacs) & \\
    PREEQTIME & Pre-equilibrate time simulated before the uploaded trajectory in nanoseconds. \tablefootnote{For example, if you upload 100-200 ns part of total 200 ns simulation, this should value should be 100.} & \\
    TIMELEFTOUT & Equilibration period in the uploaded trajectory that should be discarded in analyses. \tablefootnote{For example, if you upload 0-200 ns part of total 200 ns simulation where the first 100 ns should be considered as an equilibration, this value should be 100.} \\
    COMPOSITION & Molecules names used in the simulation and corresponding mapping files (see section \ref{naming}) & \\
    DIR\_WRK & Temporary working directory in your local computer. \\
    UNITEDATOM\_DICT & Information for constucting hydrogens for united atom simulations, empty for all atom simulations & \\
    TYPEOFSYSTEM & Lipid bilayer or something else & \\
    \hline
    PUBLICATION & Give reference to a publication(s) related to the data. & User given (optional)\\
    AUTHORS\_CONTACT & Name and email of the main author(s) of the data. & \\
    SYSTEM & System description on free text format & \\
    SOFTWARE\_VERSION & Version of the used software & \\
    FF & Name of the used force field & \\
    FF\_SOURCE & Source of the force field parameters, e.g, CHARMM-GUI, webpage, citation to a publication, etc. & \\
    FF\_DATE &  Date when force field parameters were accessed on the gives source (day/month/year). & \\
    FF{molename} & Molecule specific force field information, e.g., water model with FFSOL and sodium parameters with FFSOD. & \\
    CPT & Name of the Gromacs checkpoint file. & \\
    LOG & Name of the Gromacs log file. & \\
    TOP & Name of the Gromacs top file. & \\
    GRO & Name of the Gromacs gro file. & \\
    \hline
    TRAJECTORY\_SIZE & Size of the trajectory file in bytes & automatically extracted data. \\
    TRJLENGTH & Lenght of the trajectory (ps). & \\
    TEMPERATURE & Temperature of the simulation. & \\
    NUMBER\_OF\_ATOMS & Number of atoms in the simulation. & \\
    DATEOFRUNNIG & Date when added into the databank & \\
    EXPERIMENT & Potentially connected experimental data & \\
    COMPOSITION & Numbers of lipid molecules (NPOPC, NPOPG, etc.) per membrane leaflet are calculated by determining on which side of the center of mass of the membrane the center of mass of the head group of each lipid molecule is located.
    Numbers of other molecules such as solvent and ions (NSOL, NPOT, NSOD, etc.) are read from the topology file. & \\
    \end{tabular}
    \caption{Keys stored in the README.yaml files of simulations.}
    \label{tab:READMEkeys}
\end{table}

@@

\begin{table}[]
    \centering
    \begin{tabular}{  p{5.0cm}  p{10.0cm}}
    \toprule
    key & description \\
    \midrule
    DOI & DOI of the publication related to the experimental data. \\
    TEMPERATURE & Temperature of the experiment. \\
    MOLAR\_FRACTIONS & Dictionary of molar fractions of bilayer components \\
    ION\_CONCENTRATIONS & Dictionary of ion concentrations of the system \\% (defined as ??) \\
    TOTAL\_LIPID\_CONCENTRATION & Total concentration of lipid components. If exact concentration is not known, but experiments are performed in excess water, 'full hydration' can be given. \\
    COUNTER\_IONS & Type of counter ions if present.
\end{tabular}
    \caption{Keys stored in the README.yaml files of experiments.}
    \label{tab:READMEkeysEXP}
\end{table}

@@

\subsection{Molecule and atom naming convention} \label{naming}
